Follow-up Samples

### 2016-12-06 submission/manuscript_outline_20161024.Rmd
manuscript update discssion

## Discussion
In this study we show that the overall community structure as measured by different alpha diversity metrics, shows very little change between controls and those with either adenoma or carcinoma [Table S1] in our larger training set.  With respect to the follow up sample group there was very little difference in magnitude of change in the thetayc distance metric between those with adenoma or carcinoma[Figure 1a].  FIT had a large change in the initial and follow up samples in the carcinoma group versus the adenoma [Figure 1b].  An NMDS showed that there was very little change between initial and follow up for the adenoma group but there was a change in the carcinoma group [Figure 2].  This information showed that the removal and treatment of carcinoma for these cursory metrics had the largest response.  Yet these metrics alone would not be able to identify differences in adenomas.

>>>>

## Discussion
In our training set we show that the overall community structure as measured by different alpha diversity metrics, shows very little change between controls and those with either adenoma or carcinoma [Table S1].  With respect to our test set there was very little difference in magnitude of change in the thetayc distance metric between those with adenoma or carcinoma [Figure 1a].  In contrast, FIT had a large change in the initial and follow up samples in the carcinoma group versus the adenoma [Figure 1b].  An NMDS showed that there was very little observable change between initial and follow up for the adenoma group but there was one for the carcinoma group [Figure 2].  This cursory information is suggestive that treatment of carcinoma, had the largest response.

### 2016-12-06 submission/manuscript_outline_20161024.tex
manuscript update discssion

In this study we show that the overall community structure as measured
by different alpha diversity metrics, shows very little change between
controls and those with either adenoma or carcinoma {[}Table S1{]} in
our larger training set. With respect to the follow up sample group
there was very little difference in magnitude of change in the thetayc
distance metric between those with adenoma or carcinoma{[}Figure 1a{]}.
FIT had a large change in the initial and follow up samples in the
carcinoma group versus the adenoma {[}Figure 1b{]}. An NMDS showed that
there was very little change between initial and follow up for the
adenoma group but there was a change in the carcinoma group {[}Figure
2{]}. This information showed that the removal and treatment of
carcinoma for these cursory metrics had the largest response. Yet these
metrics alone would not be able to identify differences in adenomas.

>>>>

In our training set we show that the overall community structure as
measured by different alpha diversity metrics, shows very little change
between controls and those with either adenoma or carcinoma {[}Table
S1{]}. With respect to our test set there was very little difference in
magnitude of change in the thetayc distance metric between those with
adenoma or carcinoma {[}Figure 1a{]}. In contrast, FIT had a large
change in the initial and follow up samples in the carcinoma group
versus the adenoma {[}Figure 1b{]}. An NMDS showed that there was very
little observable change between initial and follow up for the adenoma
group but there was one for the carcinoma group {[}Figure 2{]}. This
cursory information is suggestive that treatment of carcinoma, had the
largest response.
